---
title: "Kinds of iris flowers by petal length and sepal length"
author: "Arturo Penas Rial"
date: "26/11/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## scatter

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=5}
library(dplyr)
library(plotly)
library(ggplot2)

x <- list(title = "Sepal (Length)")
y <- list(title = "Petal (Length)")

plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color=~iris$Species, mode='markers', type = "scatter") %>% 
    layout(xaxis = x, yaxis = y, title = "Kinds of iris flowers by petal length and sepal length")
```

## scatter3d

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=5}
library(plotly)

x <- list(title = "Sepal (Length)")
y <- list(title = "Petal (Length)")

plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, z = ~Petal.Width,
    type = "scatter3d", color=~iris$Species, mode='markers') %>% 
    layout(xaxis = x, yaxis = y, title = "Kinds of iris flowers by petal length and sepal length")
```

## Summary

- We will work with a well known dataset in data analysis called **Iris**.
- The dataset is composed of 150 observations of flowers of the iris plant.
- There are three kinds of iris flowers: virginica, setosa and versicolor.
- The variables or attributes that are measured for each flower are: a) The type of flower as a categorical variable, b) The length and width of the petals in cm as numerical variables, c) The length and width of the sepal in cm as numerical variables,
- 
- The plot include kinds of iris flowers by petal length and sepal length for explore the data with cool features of **plotly**.

